% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{Wood2000}
R.~Wood, \emph{The feasibility of magnetic recording at 1 terabit per square
inch}, IEEE Trans. Magn., vol. 36, pp. 36–42, Jan. 2000.

\bibitem{Rottmeyer}
R.~Rottmeyer et al., \emph{Heat-assisted magnetic recording}, IEEE Trans.
Magn., vol. 42, no. 10, pp. 2417–2421, Oct. 2006.

\bibitem{Terris}
B.~Terris, T. Thomson, and G. Hu, \emph{Patterned media for future magnetic
data storage}, Microsyst. Technol., vol. 13, no. 2, pp. 189–196, Nov.
2006.

\bibitem{Wood2009}
R.~Wood, M. Williams, A. Kavcic, J. Miles, \emph{The Feasibility of Magnetic Recording at 10 Terabits Per Square Inch on Conventional Media}, IEEE Trans. Magn., vol. 45, pp. 917-923, Feb. 2009.

\bibitem{ASTC}
ASTC Technology Roadmap - 2014 v8, \url{http://idema.org/?page_id=416}, 2014.

\bibitem{HGST}
\emph{Perpendicular Magnetic Recording Technology}, HGST, a Western Digital company, Nov, 2007.

\bibitem{Krishnan}
A.~Krishnan, R.~Radhakrishnan, B.~Vasic, A.~Kavcic, W.~Ryan, F.~Erden,
\emph{2-D Magnetic Recording: Read Channel Modeling and Detection}, IEEE Trans. Magn., vol. 45, pp. 3830-3836, Oct. 2009.

%\bibitem{Feldman}
%T.~Feldman, G.~Gibson, 
%\emph{Shingled Magnetic Recording}, IEEE Trans. Magn., vol. 45, pp. 3830-3836, Oct. 2009.

\bibitem{Gibson}
G.~Gibson, G.~Ganger, 
\emph{Principles of Operation for Shingled Disk Devices}, Technical Report
CMU-PDL-11-107. CMU Parallel Data Laboratory. http://repository.cmu.edu/pdl/7. Apr. 2011.

\bibitem{Toshiba_BPM}
Bit-Patterned Media for High-Density HDDs, \url{http://www.toshiba.co.jp/rdc/rd/fields/11_e09_e.htm}.

\bibitem{IEEE_BPM}
B. Patterned Media, \url{http://ieeexplore.ieee.org/ieee_pilot/articles/96jproc11/jproc-EDobisz-2007600/article.html}

\bibitem{IEEE_HITACHI}
Shingled Magnetic Recording and Two-Dimensional Magnetic Recording, \url{http://www.ewh.ieee.org/r6/scv/mag/MtgSum/Meeting2010_10_Presentation.pdf}, Oct. 2010.

\bibitem{Elidrissi}
R.~Elidrissi, Ch.~Kheong, Y.~Zhimin,
\emph{A Study of SMR/TDMR With a Double/Triple Reader Head Array and Conventional Read Channels}, IEEE Trans. Magn., vol. 50, pp. 24-30, Mar. 2014.

\bibitem{Krishnan}
A.~Krishnan, R.~Radhakrishnan, B.~Vasic, A.~Kavcic,
\emph{2-D Magnetic Recording: Read Channel Modeling and Detection}, IEEE Trans. Magn., vol.45, no.10, pp.3830-3836, Oct. 2009.

\bibitem{Vasic}
B.~Vasic, M.~Khatami, Y.~Nakamura, Y.~Okamoto, Y.~Kanai, J.~R.~Barry, S.~W.~McLaughlin, E.~B.~Sadeghian
\emph{A Study of TDMR Signal Processing Opportunities Based on Quasi-Micromagnetic Simulations}, IEEE Trans. Magn., vol.51, no.4, pp.1-7, Apr.2015.

\end{thebibliography}
